\documentclass[12pt]{article}
\setlength{\textheight}{9.80in}
\setlength{\textwidth}{6.40in}
\setlength{\oddsidemargin}{0.0mm}
\setlength{\evensidemargin}{1.0mm}
\setlength{\topmargin}{-0.6in}
\setlength{\parindent}{0.2in}
\setlength{\parskip}{1.5ex}
\newtheorem{defn}{Definition}
\renewcommand{\baselinestretch}{1.2}

\begin{document}

\bibliographystyle{prsty}

\thispagestyle{empty}

\title{{\it Dors1}: Building an Atmosphere}

\author{C. Godsalve \\
email:{\tt seagods@hotmail.com} }

\maketitle

\tableofcontents

\section{A First Run of {\it Dors1 -v}}

To do any radiation calculations in a ``one dimensional" atmosphere, we 
require an atmosphere consisting of discrete
layers or ``slabs". 
Each layer must have an {\it optical depth}, a {\it single scattering albedo}, 
 a {\it phase function} and a temperature profile. {\it Dors1} has the job of creating a
data file containing all this information. If the you are unfamiliar with these terms you need
to consult a standard textbook on radiative transfer such as by Chandrasekhar \cite{Chandrasekhar:Mybib},
 Goody and Yung \cite{GoodyYung:Mybib}, or Liou \cite{Liou:Mybib}.

The program that sets up
the atmosphere for doing radiative transfer calculations is {\it Dors1}. This can build
the atmosphere in two entirely different ways. It can build an arbitrary atmosphere
or a model of the Earth's atmosphere. The arbitrary atmosphere is determined
completely by the user: we shall mainly consider
building up a layered Earth atmosphere from realistic data. 

The data used by {\it Dors1} are based on
the 1976 U. S. Standard Atmosphere \footnote[1]{All the references to the the U. S. Air Force
Geophysical library are available from http://www.dtic.mil/dtic/}  \cite{USStandard:Mybib} and its supplements, especially 
the AFGL constituent
profiles up to 120km \cite{ConstProfs:Mybib}.

Once compiled, the best way to start using {\it Dors1} is just to type {\it Dors1 -v [ENTER]} at a system terminal.
(If you are used to the command line, then hitting the [ENTER] key is obvious, and we omit
it in the rest of this article.)
The { \it -v} stands for ``verbose mode".
 In this mode you will be prompted for all the required
inputs and given explanations as to what these inputs mean. When {\it Dors1} has finished, it will write a record of what you entered 
 in the file named  {\it Dors1in.dat} (unless otherwise specified).  It isn't a bad idea to make a copy of this file to something 
like {\it example.Dors1in.dat}.
If, at some later stage, you wish to make a modification, you can just edit 
{\it Dors1in.dat}. Once you have had some experience of the verbose input, making edits should be
easy.
Now you have created or edited {\it Dors1in.dat}
 you may just type {\it Dors1}. This will read {\it Dors1in.dat} and build an 
atmosphere according to the contents of {Dors1in.dat}. You may have many different input files, each named say {\it Dors1inX.dat}, say. Just type
``{\it Dors1 Dors1inX.dat}" instead. 

On typing {\it Dors1 -v} the first thing you will be prompted for is whether you want to build
an Earth atmosphere or an arbitrary atmosphere. We shall look only at an Earth atmosphere
for most of this article, so for now, we always give the number 1 as a response. 

Dors1 automatically splits up an Earth type atmosphere into four distinct regions.
These four different regions are needed because of atmospheric aerosols. In the lower
kilometre of atmosphere or so, we may have different types of boundary layer
aerosols. From a couple of kilometres
up to the stratosphere, we have tropospheric aerosols, and in the stratosphere we may have
volcanic aerosols. The aerosols in the atmosphere above the stratosphere are different again.
These regions follow the example of older atmospheric radiation codes called {\it LOWTRAN 7}
\cite{LOWTRAN:Mybib}, and  {\it MODTRAN 5} \cite{MODTRAN:Mybib}.
If it were not for differing aerosol types, with different scattering and spectral properties,
we would not need these four distinct regions. Including atmospheric aerosols is not a simple
matter, and we leave a thorough discussion of them for later.

This is not to say we could treat  an atmosphere as a single layer were it not for aerosols.
Various molecules in the Earth's atmosphere have absorption spectra, and these spectra
depend on the temperature and the pressure which vary with height, as does the mixing ratio
of various molecules.
In order to capture this, we must subdivide the atmosphere into ``slabs" where the temperature and
the pressure do not vary too much. The need for the aerosol regions is less in the thermal infrared
than the other spectral regions, but they are used throughout the full spectral range. 

So, let us have a ``run through" of {\it Dors1} -v. Recall that the  first question was as to
whether you want an Earth
atmosphere, or some other user defined atmosphere. We have entered the number one to select
an Earth atmosphere. The next question concerns how we are to enter the amount of tropospheric
and boundary aerosol. We are asked whether we want to enter optical depths or a visibilities.

If we have estimates of the optical depths of the upper
troposphere and the boundary layer then we can choose the option to enter these optical depths. Now, the extinction coefficient of any aerosol depends on the wavelength. The optical depth to be entered is the optical depth at a wavelength
of $0.55\mu m$, and the particular aerosol model is used to calculate optical depths at other wavelengths. Again, more detailed discussions of aerosols are given later.


Otherwise we may enter a ``visibility" (or more accurately a {\it meteorological range}) in kilometres.
The more aerosol there is, the lower the visibility. On a very clear day we can see tens of kilometres.
 On a very hazy day, things that are only a couple of kilo meters away are obscured by haze. In
this way, the we have a fairly intuitive grasp of what kind of values to enter. If visibility
is chosen, then the actual optical depth (at $0.55 \mu m$)
 is calculated via Koschmieder's empirical formula
 as used in \cite{Longtin_etal:Mybib} for example.

At this point we must give {\it Dors1} wavelength information. What you need to do is enter
two  wavelengths covering a range. That is, suppose we want to look at the wavelength
range 0.6 to 0.7 micrometres, we enter the smaller wavelength ($\lambda_1)$ of 0.60 and the larger
wavelength ($\lambda_2)$ of 0.7. These two wavelengths can be the same if the user chooses them to be so.
In this case  {\it Dors1} will output the necessary data for a single wavelength calculation.
 However for most
practical purposes some kind of wavelength range is needed. 

Suppose we have a  wavelength range which is sufficiently small, and know that 
 there are no  molecular absorption lines in this range: then we need only a single wavelength. 
In this case we enter two identical wavelengths. By ``sufficiently small" we mean that the wavelength range is
small enough so that the aerosol phase function, single scattering albedo, and optical depth,
 do not change in any significant way over the range. (The same goes for Rayleigh optical depth and the ground
reflectance spectrum). It is
up to you to familiarise yourself with aerosol data supplied with the {\it Dors} so you can see
whether or not a single wavelength will do. I hope you will find
that the graphs supplied in this document make such decisions as easy as possible.

Unfortunately, whenever there are many sharp features over a given wavelength
range, such as molecular absorption lines, we cannot use a single wavelength approximation.
The {\it Dors} uses a correlated-$\kappa$ approach in this case. Band models are an alternative,
and when multiple scattering calculations are required, these can be converted
to correlated-$\kappa$ distribution functions \cite{Goody:Mybib}, \cite{Domoto:Mybib}, and
 \cite{GodsalveBand:Mybib}.
Detailed explanations of the correlated-$\kappa$ method are given in \cite{GoodyWest:Mybib}, 
\cite{LacisOinas:Mybib}, \cite{FuLiou:Mybib}, and \cite{RoseKratz:Mybib}. The {\it Dors} does not use
band models, and {\it Dors1} tailors the correlated-$\kappa$ method to an instrument response
function specified by the user in a file which for has the default name {\it myresp.dat}.
 ({\it Dors1} shall not look for this input file if the two wavelengths
are equal. In this case you don't need to create the file.)

If you have a different name for the response function data file, just 
type ``{\it Dors1 Dors1inX.dat respX.dat}" where {\it respX.dat} is whatever
your response function file name is. For now, you have to use the default when running {\it Dors1} in verbose
mode. (When calling the {\it Dors} via shell scripts it will be useful to have different input file names,
 but you would hardly write a script  running  many instances of {\it Dors1} in verbose mode, would you?)

 The ``myresp.dat"  file  shall
consist of one line specifying the number of points $n$,
 followed by $n$ lines consisting
of wavelength-response function pairs. The response function should integrate to unity
between the two specified wavelengths. (It shall be normalised within {\it Dors1} if
it doesn't integrate to unity, and a warning will be output.)

Now, you may not have any instrument in mind. If, for instance, you want to know the Top Of Atmosphere (TOA) 
reflectance of a model atmosphere rather than model an instrument's measurement of it, what do you do?
In this case you specify just enter a constant value for the response function. It should be equal
to $1/(\lambda_2-\lambda_1)$. (It will be normalised internally anyway, but
it is preferable for numbers in the file containing the response function data to be the
actual numbers used internally.)

After you have entered the wavelengths, you are prompted to enter how many layers each of
the four main aerosol regions are to be split into. If you just want four slabs one for
each aerosol region, enter one for each region. You can choose any number of slabs for
each aerosol region you like. Note that this also affects the molecular spectra used
because of temperature and pressure variations of the absorption line widths. You need to
gain experience of how this affects the radiation calculations.

After this you are prompted to select one of 6 pre-defined atmospheres, or a``user defined" atmosphere.
The six pre-defined atmospheres  are tropical, mid latitude Summer and Winter, and 
sub-Arctic Summer or Winter, and finally
the U. S. 1976 standard. 
Now, the tropospheric and stratospheric aerosol models are 
dependent on the season, whereas the tropical and standard atmospheres are not. 
Because some aerosols are seasonal you are prompted as to whether you want to use
 ``Spring/Summer" or ``Autumn/Winter". 
Once you have chosen, you are prompted for tropical, mid-latitude, Sub-Arctic, standard,
 or user defined.

Now, some users might want to look at the interaction 
 between Rayleigh scattering and scattering from aerosols. To help with this we have the option
of switching either of these off. Normally, neither will be switched off, and you just select
zero when prompted as to  whether or not switch off Rayleigh scattering, and then the same
 for aerosol scattering.

Next, we are asked to enter numbers that tells {\it Dors1} what aerosol extinction profiles
and phase functions to use for the upper atmosphere, the stratosphere, and the boundary layer.
The user is prompted with a list of available types and the number that is to be entered to
choose that type.

Now, the next section is about water vapour. This is the most variable of all the
constituents in the atmosphere.  Each of the first six atmospheres has a different number
density of water molecules as a function of height. You might, however, want to choose your
own --- but  without going to the length of defining your own atmospheres.  One way one 
might want to do this is by defining a humidity profile. {\it Dors1} enables you to do 
this and you are asked whether you want to use the defaults as defined in the six pre-defined
atmospheres, or override the pre-defined profile for water vapour while still using
the pre-defined profiles for temperature and pressure. For now, just enter one to select the
pre-defined profile.

Pressure and temperature at the ground are also highly variable. The user can ``tweak" the
pre-defined profiles to take this into account. You are prompted as to whether you have ground pressure
and/or temperature data. You will be prompted further if you say you do. If you enter
your own ground pressure that is say, 1.05 times the pressure at the ground
in the chosen profile, this will scale the entire column pressure by 1.05. If you enter a ground
temperature, this will just change the ground temperature in the temperature profile. For now, just
enter zero so that the pre-defined profiles are unchanged.

It is envisaged that you might want to use the {\it Dors} to simulate aircraft remote sensing
experiments as does 6S \cite{6S:MyBib}. The radiative transfer calculations are all done
in terms of optical depth, so {\it Dors1} will need to find where the aeroplane is
in terms of optical depth as calculated from the aeroplane height (above Sea level and in km). If you select
aeroplane remote sensing (1) you are prompted for a height. Select zero for now.

Other things that may vary are the height of the ground, the thickness of the boundary layer,
 the height of the troposphere, and so on. You are next prompted as to whether you want to
use the default heights or enter your own. For now select the default.

The last thing that we are prompted for is the order of the Gauss quadrature rule.
This is the rule that calculates integrations in height in each sub-layer of each
aerosol region. This is another thing that you need to experiment with. For now, just choose 4.
(The minimum is two.)

We have now finished, we have a record in {\it Dors1in.dat}. Look at the following example.
\begin{verbatim}
1 
1 45.000000 26.000000
0.500000 0.600000 
1 2 3 4
1
0 0
13 6 3 1 0
1 0 -1000000.000000 -1.000000
0 -1000000.000000
1 0.000000 2.000000 10.000000 30.000000 120.000000
4 
\end{verbatim}
In the first line, we have chosen an Earth atmosphere. Then we see we have chosen
to enter visibilities and chosen a tropospheric visibility of 45km and a boundary layer visibility
of 26km. Our start wavelength is 0.5$\mu m$ and our stop wavelength is $0.6 \mu m$. The
upper atmosphere is just 1 slab. The stratosphere is split into two slabs, the upper
troposphere is split into three slabs and the boundary layer is split in four.

On the next line we see the numbers 13, 6, 3, 1, 0.
The value of 13 shows we have a normal upper atmosphere. Other values might be 14 for ``transition
from volcanic to normal", 15 for ``transition from volcanic to extreme volcanic", and 16 for
 ``extreme volcanic". Then the value of 6 means we have chosen ``Background volcanic Spring/Summer".
We could have chosen 8, 10, or 12 for ``Moderate volcanic", ``High Volcanic", or "Extreme volcanic".
If we had chosen Autumn/Winter, the corresponding option numbers would have been 5, 7, 9, and 11.

After the numbers 13 and 6, we see a 3. This determines the tropospheric aerosol.
In verbose mode, there is no input number required for the tropospheric aerosol type.
However when run without the verbose option, {\it Dors1} requires that  the troposphere type should be 3 or 1.
It should be 3 for Spring/Summer and 1 for Autumn/Winter. In the example using verbose mode
the output {\it Dors1in.dat} file has the number 3 since we chose Spring/Summer.
 The boundary aerosol type is 1 for ``rural".
What is that zero at the end? If we chosen the ``Maritime/Ocean" option we would have
been prompted for which of these two it was. A number has to be there regardless of what option
we choose for the boundary layer. If we choose 3 for the boundary layer option, this last number is
either 1 for open Ocean, or 0 for Maritime.

The next line indicates that we have chosen 1 for the default water vapour profiles, and zero
 as far as knowing temperature and pressure. But there are still two (silly) numbers for
temperature and pressure. These have to be there regardless, even though in this case
they are not to be used. (Make them negative to make it obvious they are not used.)
Similarly, the next line has a zero to indicate that we are not simulating an aeroplane.
Nevertheless, we must include a height on this line which we have made a large negative
value to make it clear it isn't used in this case.

The next line starts with a 1, indicating that we are using the default heights (in km) for
the ground, the boundary layer, tropopause, stratopause, and Top Of Atmosphere (TOA).
This is followed by four numbers. If you are using the defaults, these numbers {\it must be}
the default values of 0, 2, 10, 30, and 120.

The last line is just the order of the Gauss quadrature rule for vertical integration.
So, we have finished our ``run through" of {\it Dors1}. Next we shall begin to see what {\it Dors1}
actually does.

\section{The Treatment of the Atmospheric Data}

We have seen we have six default atmospheres to choose from. The first is tropical, the next four
are mid latitude (45N) and sub-Arctic (60N)  Summer and Winter, then the last is the U. S. 1976 standard 
atmospheres. In these atmospheres, the only constituent profiles that depend on latitude or
whether it's Summer or Winter are Carbon dioxide , Ozone, Nitrous oxide, and methane. The height
 dependence of all the other atmospheric constituents are just those of the 1976 standard.
Clearly things such as methane are highly variable, so there is a separate user defined option
for these four atmospheric. However, to quote \cite{ConstProfs:Mybib} ``Molecules 8-28 are provided
as single representative profiles. Their natural variability can be very different from the selected 
profiles." If, for instance you want to experiment with the profiles, just overwrite the ones provided
with your own! The {\it Atmospheres} directory contains a sub-directory called {\it StartMols}. This contains
a copy of all the profiles that {\it Dors1} came with. Once you have finished, you can just overwrite
 the profiles with their originals. 

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Number & Molecule & Name & Number & Molecule & Name \\ \hline
1 & H2O & Water Vapour & 15 &HCl & Hydrochloric acid  \\ \hline
2 & CO2 & Carbon dioxide & 16 & HBr & Hydrogen Bromide\\ \hline
3 & O3 & Ozone & 17 & HI & Hydrogen iodide \\ \hline
4 & N2O & Nitrous oxide & 18 & ClO & Chlorine monoxide \\ \hline
5 & CO & Carbon monixide & 19 & OCS & Carbonyl sulphide\\ \hline
6 & CH4 & Methane   & 20 & H2CO & Formaldehyde \\ \hline
7 & O2 & Oxygen & 21 & HOCl & Hypochlorous acid\\ \hline
8 & NO & Nitric Oxide & 22 & N2 & Nitrogen\\ \hline
9 & SO2& Sulphur Dioxide &23 & HCN &  Hydrogen Cyanide\\ \hline
10 & NO2 & Nitrogen Dioxide & 24 &  CH3Cl & Methyl chloride\\ \hline
11 & NH3 & Ammonia & 25 & H2O2 & Hydrogen peroxide\\ \hline
12 & HNO3 & Nitric acid & 26 & C2H2 & Acetylene\\ \hline
13 & OH & Hydroxyl radical & 27 &  C2H6 & Ethane \\ \hline
14 & HF & Hydrogen Fluoride & 28 & PH3 & Phosphene\\ \hline
\end{tabular}
\caption{The 28 AFGL Gaseous Constituents}
\end{center}
\end{table}

The molecular species 1- 28 in the {\it Dors} are numbered as in the 1976 standard. For completeness, we
include a table of what the species are, and their numbers.
We are using the HITRAN \cite{RothmanETAL:Mybib} database to calculate molecular absorption.
HITRAN includes data on more molecules in the original AFGL list  (molecules 29-39).
I have no idea as to what the concentrations of these extra molecules
 are as a function of height, however I have
included ``dummy" profiles for the extra gases included in HITRAN. Most likely, you won't
bother with them at all.
\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Number & Molecule & Name & Number & Molecule & Name \\ \hline
29 & COF2& Carbonyl Flouride & 35 &ClONO2& Chlorine Nitrate\\ \hline
30 & SF6 & Sulphur Hexaflouride & 36 & NO+& Ionised Nitric oxide\\ \hline
31 & H2S & Hydrogen sulphide & 37 & HOBr & Hypobromous acid \\ \hline
32 & HCOOH & Formic acid& 38 & C2H4& Ethylene \\ \hline
33 & HO2 & Hydroperoxyl radical& 39 & CH3OH & Methanol\\ \hline
34 & O  & Atomic Oxygen&  & & \\ \hline
\end{tabular}
\caption{Extra Constituents in HITRAN}
\end{center}
\end{table}

Many of these 39 gases are negligible as far as the absorption of radiation is concerned.
You should be able to see a small file called {\it GasMask.dat}. This consists
of pairs of lines,
The first line in each pair consists  of the molecule number. So line 1 has numbers 1 to 10
 (from H2O to NO2 inclusive). The second
 second line  consists of 10 ones and zeros. A zero means ``ignore this gas
altogether". For many purposes only the first seven molecules of line 2 should be one, and the rest of the gases
can be ignored.


\section{Aerosol Models}

Though users may define their own aerosol models, we have performed the Mie calculations on several standard 
aerosol models. These models have been used in LOWTRAN,  MODTRAN, 6S, and elsewhere, and may be regarded as the default aerosol models for the DORS also. We shall go into some detail as to the origin of the models and the extensive
 Mie calculations based on these models done by the author here.

First, by aerosol, we mean any particulate matter suspended in the air. As such, this particulate matter can
both scatter and absorb radiation. In general, many of these particles will not be spherical. However, some will be
close to spherical 
under some circumstances, and we shall use scattering from spheres as a numerical model. The spheres are to
considered as being far apart in terms of wavelength, and so the scattering is considered to be independent. By
this we mean that the local electric fields generated by the incoming radiation in one sphere do not affect
any other sphere: only the far field matters.

To model scattering from a single sphere requires the complex refractive index of the material, the radius of
the sphere, and the wavelength of the light. However, there shall be a whole range of particle sizes. Therefore
we need a probability distribution function (or pdf) for the spheres that make up our model scatterers.
The problem of scattering from such a {\it spherical polydispersion} was first investigated extensively
by Deirmendjian \cite{Deirmendjian:Mybib}. If the reader comes across terms as ``haze-M'' or ``cloud-C" they are all defined by
Deirmendjian. However, in subsequent years, much investigation was done into the size distribution, composition, 
 refractive index (as a function of wavelength) of atmospheric aerosols.
Our default aerosols are due to the work of Shettle, Fenn, and many others. These may be deemed as ``out of date"
 by some users, which is why users have the option of incorporating aerosols defined
 by their own data and scattering models.

We shall begin with the {\it rural} aerosol as defined by Shettle and Fenn \cite{ShettleFenn2:Mybib}. First we write down
the standard form of the {\it lognormal} distribution.
\begin{equation}
\rho(r,\mu)=\frac{ e^{-\lbrack (ln r-\mu)^2/2 \sigma^2 \rbrack} }{ r \sigma \sqrt{2 \pi}}.
\end{equation}
Here $\mu$ is the log of the mode radius $r_m$. The skewness of the distribution
 increases with the standard deviation $\sigma$.
The moments are given by
\begin{equation}
\mu_k= \int_0^\infty r^k \rho(r) dr=e^{\mu k +k^2 \sigma^2},
\end{equation}
The rural aerosol is bi-modal, and {\it both modes} consist of two types of aerosol. One is a water
soluble aerosol, and the other is ``dust like".
 Now, in \cite{ShettleFenn2:Mybib} the two mode radii $r_m$ are 0.005$\mu m$
and $0.5 \mu m$ respectively. The pdf for the bimodal distribution is just
\begin{equation}
\rho(r,\mu_1, \mu_2)=\alpha \rho(r, \mu_1)+\beta \rho(r, \mu_2)
$$   $$
\alpha+\beta=1, \> \alpha >0,  \> \beta >0.
\end{equation}
In this paper, the values of $\alpha$ and $\beta$ were $1-2.5 \times 10^{-6}$ and $2.5 \times 10^{-6}$.
The casual reader might think these vastly different values mean that the large mode radius part
of the distribution can be ignored. However, a rough rule of thumb is that the scattering cross
section grows with the square of the particle size, so the small proportion of large particles may 
scatter as much light as the large proportion of small scatterers.

In a later paper Shettle and Fenn \cite{ShettleFenn:Mybib} look at the effect of humidity on the rural aerosol.
The water soluble type of aerosol will grow in size as the humidity increases.
Such an aerosol is called {\it hygroscopic}.
The first difference is that the small mode radius is now much larger,  and the value
of $\beta$ has increased to $1.25 \times 10^{-4}$. The author believes these latter figures are
 nearer to an accurate description. 
 Now, for the rural aerosol the following numbers appear in \cite{ShettleFenn:Mybib}.
\begin{center}
\begin{tabular}{| c | c | c | }
\hline
Relative Humidity&  $r_1 \mu m$ & $r_2 \mu m$ \\
\hline
 0 \% &  0.02700 & 0.4300 \\
 50\% &  0.02748 & 0.4377 \\
 70\% &  0.02846 & 0.4571 \\
 80\% &  0.03274 & 0.5477 \\
 90\% &  0.03884 & 0.6462 \\
 95\% &  0.04238 & 0.7078 \\
 98\% &  0.04751 & 0.9728 \\
 99\% &  0.05215 & 1.1755 \\
\hline
\end{tabular}
\end{center}
Now these radii are for the rural aerosol, which is defined to be a non
 hygroscopic aerosol (30\% dust like) and the hygroscopic water soluble aerosol
(70\%) which grows with increasing humidity.
 Suppose we  take the 99\% values, we {\it might}  take this to mean that
 $0.05215=0.7 r_h+0.3 r_{dry}$. That is to say we might take the mode 
radius of the dust (which doesn't grow with humidity) to be the same
 as the dry mode radius
of the water soluble aerosol, and then take the mode radius of the aggregate
to be a weighted sum of the swollen hygroscopic aerosol and the dry dust aerosol.
 In which case, we would have $r_h=0.06293 \mu m$
for the small particle mode
 and $1.495 \mu m$
for the large particle mode. (Incidentally, hygroscopic aerosols can display
hysteresis \cite{Samparta:Mybib}, so knowledge of the humidity doesn't necessarily give
us a very good handle on the size parameter.)

There is further confusion here: the hygroscopic aerosol is taken to be a mixture
 of ammonium sulphate, calcium sulphate, and ``organic matter". The complex
refractive index of ammonium sulphate aerosol and ``water soluble" aerosol is tabulated.
It is clear from the data that ammonium sulphate is not in the mixture for water
soluble aerosol (or that it is a negligible proportion --- which is unlikely.)
It is unclear whether ``water soluble" {\it is} calcium sulphate or some mixture
which may or may not include calcium sulphate.

Also though ammonium sulphate is readily soluble, calcium sulphate
is only weakly soluble. So if calcium  sulphate aerosols grow with humidity, they must
act (mostly) as a solid core surrounded by a weak solution of of calcium sulphate.

So, how is one to use Mie theory with this data in order to obtain the model
optical properties of the aerosol? Ideally, we would need want the complex
refractive index as a function of wavelength and size distribution of each and every component.
Not only this, we would want to know the details of how each hygroscopic component
changes with humidity.


From HITRAN,  tables for the complex refractive index as a function of wavelength
are published for the water soluble component, dry ammonium sulphate, and a ``dust like" component
and  water contained in the file named ``Shettle.dat".  The data for
the water soluble component are for the dry aerosol. However as the
aerosols grow, they have more and water content. As we do the Mie
calculations for different humidities, we need the refractive index of a mixture
of  water and the dissolved water soluble aerosol. 


We use Shettle and Fenn's parametrisation of the
{\it water activity} $a_w$ which is related to the surface tension as 
a function
of the particle radius. This radius is in itself a function of the water
 activity. We have
\begin{equation}
a_w=H \exp \left ( -\frac{0.31469}{r(a_w) T)} \right).
\end{equation}
Here $H$ is the humidity scaled to (0,1), $T$ the absolute temperature, and $r$ is the particle
size in micrometres.
On top of this we have
\begin{equation}
r(a_w)= r_{dry}\sqrt[3]{1+\rho \frac{ m_w(a_w)}{m_{dry}}}
\end{equation}
These equations were solved for the ``wet radius" $r_w$ using data tabulated by H\"anel \cite{Hanel:Mybib}. Then Shettle and Fenn
use
\begin{equation}
n=n_w+(n_{dry}-n_w) \left ( \frac{r_{dry}}{r_h} \right )^3.
\end{equation}
This is the resulting refractive index for a completely dissolved mixture. 
(Which is hardly possible for calcium sulphate.)

So: it is not clear how Shettle and Fenn proceeded, but they say ``To reduce the
calculations for the current models, which now are done as a function of
humidity, the individual aerosol particles are considered to be a homogeneous
mixture of the different types of substance - as many natural aerosols are. The
resulting  refractive index for the composite rural aerosol is given
 in Table 4a and 4b." 

However they go on to say that Bergstrom has argued that using such mean 
refractive indexes  in determining the optical properties will result in errors. Shettle and 
Fenn indicate they have made calculations indicating that the errors
are acceptably small (~5\% with a maximum of 16\%). Oddly, although Shettle and Fenn tabulated
the rural aerosol refractive index as a function of humidity, they did not tabulate
the water soluble or ammonium sulfate aerosol refractive index as a function of
humidity.

We shall proceed by using the aggregate refractive index and mode radius 
provided by Shettle and Fenn, which we reproduce below. 

\begin{center}
\begin{table}
\begin{tabular}{| c | c | c | c | c |  }
\hline
 $\lambda \mu m$ & 0\%  & 50\%  & 70\%  &  80\%  \\
\hline
0.2000 & 1.530 -7.00e-2  & 1.523 -6.64e-2 &     1.510 -5.98e-2 & 1.471 -3.92e-2 \\
0.2500  &  1.530 -3.00e-2  &  1.521 -2.85e-2  &  1.505 -2.56e-2  &  1.456 -1.68e-2   \\
0.3300  &  1.530 -6.00e-3  &  1.521 -7.59e-3 &   1.504 -6.83e-3  &  1.450 -4.49e-3  \\
0.3371  &  1.530 -5.90e-3  &  1.520 -5.60e-3  &  1.503 -5.04e-3   & 1.449 -3.31e-3 \\
0.4000 &   1.530 -5.90e-3  &  1.520 -5.60e-3  &  1.502 -5.04e-3  &  1.446 -3.31e-3 \\
0.4880  &  1.530 -5.90e-3  &  1.520 -5.60e-3  &  1.501 -5.04e-3  &  1.444 -3.31e-3 \\
0.5145  &  1.530 -5.90e-3 &   1.520 -5.60e-3  &  1.501 -5.04e-3  &  1.444 -3.31e-3  \\
0.5500  &  1.530 -6.60e-3  &  1.520 -6.26e-3  &  1.501 -5.63e-3  &  1.443 -3.70e-3  \\
0.6328  &  1.530 -6.60e-3 &   1.520 -6.26e-3  &  1.501 -5.63e-3  &  1.443 -3.70e-3  \\ 
0.6943 &   1.530 -7.30e-3 &   1.520 -6.92e-3  &   1.501 -6.23e-3 &   1.443 -4.09e-3  \\ 
0.8600 &   1.520 -1.08e-2  &  1.510 -1.02e-2  &  1.492 -9.22e-3  &  1.436 -6.06e-3  \\ 
1.0600  &  1.528 -1.43e-2  &  1.510 -1.36e-2  &  1.492 -1.22e-2  &  1.435 -8.02e-3  \\ 
1.3000  &  1.495 -1.64e-2  &  1.486 -1.56e-2  &  1.470 -1.40e-2  &  1.419 -9.21e-3  \\
1.5360  &  1.477 -1.85e-2  &  1.469 -1.76e-2  &  1.454 -1.58e-2  &  1.407 -1.04e-2 \\  
1.8000  &  1.421 -1.43e-2  &  1.415 -1.36e-2  &  1.405 -1.22e-2  &  1.373 -8.07e-3  \\ 
2.0000  &  1.372 -8.00e-3  &  1.369 -7.65e-3  &  1.362 -6.99e-3  &  1.343 -4.97e-2 \\  
2.2500 &  1.360 -9.70e-3   & 1.357 -9.22e-3   & 1.350 -8.34e-3  &  1.330 -5.61e-2  \\
2.5000  &  1.348 -1.11e-2  &  1.344 -1.06e-2  &  1.335 -9.83e-3  &  1.310 -6.99e-2 \\  
2.7000  &  1.334 -4.24e-2  &  1.326 -1.12e-2  &  1.313 -3.90e-2  &  1.270 -3.21e-2  \\ 
3.0000  &  1.342 -1.90e-2  &  1.343 -1.20e-2  &  1.346 -5.60e-2  &  1.355 -1.30e-1  \\ 
3.2000 &   1.367 -8.60e-3  &  1.373 -1.29e-2  &  1.383 -2.09e-2  &  1.416 -4.54e-2  \\
3.3923 &   1.379 -8.80e-3  &  1.381 -9.40e-3 &   1.365 -1.05e-2  &  1.398 -1.39e-2 \\ 
3.5000 &   1.399 -6.80e-3  &  1.399 -6.03e-3  &  1.399 -7.18e-3  &  1.399 -7.94e-3  \\ 
3.7500 &   1.397 -6.20e-3  &  1.396 -5.97e-3 &   1.393 -5.72e-3  &  1.385 -4.96e-3 \\  
4.0000 &   1.397 -7.10e-3  &  1.394 -6.97e-3 &   1.390 -6.73e-3  &  1.377 -6.06e-3  \\
4.5000 &   1.400 -1.33e-2  &  1.397 -1.33e-2 &   1.390 -1.33e-2  &  1.370 -1.33e-2  \\ 
5.0000 &   1.390 -1.32e-2  &  1.387 -1.32e-2  &  1.380 -1.31e-2  &  1.361 -1.26e-2  \\ 
5.5000 &   1.374 -1.89e-2  &  1.370 -1.85e-2  &  1.363 -1.78e-2  &  1.341 -1.57e-2  \\ 
6.0000 &   1.332 -2.72e-2  &  1.329 -2.13e-2 &   1.322 -3.89e-2 &   1.303 -6.23e-2  \\ 
6.2000 &   1.343 -3.06e-2 &   1.324 -3.36e-2 &   1.346 -3.90e-2  &  1.352 -5.58e-2  \\ 
6.5000 &   1.361 -3.57e-2 &   1.360 -3.59e-2 &   1.358 -3.62e-2  &  1.351 -3.72e-2 \\  
7.2000 &   1.400 -6.55e-2 &   1.395 -6.38e-2 &   1.387 -6.06e-2  &  1.361 -5.08e-2 \\ 
\hline
\end{tabular}
\caption{Short wavelength values of the complex refractive index of the small rural aerosol mode at low humidity}
\end{table}
\end{center}

\begin{center}
\begin{table}
\begin{tabular}{| c | c | c | c | c |  }
\hline
 $\lambda \mu m$ & 0\%  & 50\%  & 70\%  &  80\%  \\
\hline 
7.9000 &   1.185 -5.75e-2  &  1.191 -5.63e-2 &   1.201 -5.40e-2  &  1.233 -4.71e-2  \\ 
8.2000 &   1.046 -9.33e-2  &  1.058 -6.93e-2  &  1.081 -6.39e-2  &  1.151 -6.71e-2  \\ 
8.5000 &   1.300 -1.78e-1 &   1.299 -1.70e-1  &  1.297 -1.57e-1  &  1.290 -1.16e-1  \\ 
8.7000 &   2.100 -2.33e-1  &  2.057 -2.23e-1  &  1.979 -2.04e-1  &  1.736 -1.47e-1   \\
9.0000 &   2.302 -3.01e-1  &  2.249 -2.88e-1  &  2.150 -2.63e-1  &  1.845 -1.86e-1  \\
9.2000 &   2.056 -3.39e-1  &  2.015 -3.24e-1  &  1.939 -2.95e-1  &  1.704 -2.08e-1   \\
9.5000 &   1.884 -1.61e-1  &  1.851 -1.55e-1  &  1.790 -1.44e-1  &  1.602 -1.10e-1   \\
9.8000 &   1.831 -1.15e-1  &  1.800 -1.12e-1  &  1.743 -1.05e-1  &  1.567 -8.56e-2  \\ 
10.000 &   1.799 -1.12e-1  &  1.769 -1.08e-1  &  1.714 -1.03e-1  &  1.544 -8.49e-2   \\ 
10.591 &   1.718 -8.50e-2  &  1.690 -8.41e-2  &  1.639 -8.24e-2  &  1.481 -7.73e-2  \\
11.000  &  1.690 -6.65e-2  &  1.662 -6.81e-2 &   1.611 -7.09e-2  &  1.454 -7.98e-2  \\
11.500 &   1.646 -6.29e-2 &   1.619 -6.70e-2  &  1.570 -7.45e-2 &   1.418 -9.76e-2   \\
12.500 &   1.587 -6.41e-2 &   1.563 -7.41e-2 &   1.519 -9.26e-2 &   1.383 -1.50e-1   \\
13.000 &   1.575 -6.85e-2 &   1.553 -8.07e-2  &  1.512 -1.03e-1  &  1.387 -1.72e-1   \\
14.000 &   1.548 -7.66e-2 &   1.531 -9.17e-2  &  1.499 -1.20e-1  &  1.400 -2.05e-1   \\
14.800 &   1.479 -1.00e-1 &   1.468 -1.15e-1  &  1.447 -1.43e-1 &   1.382 -2.30e-1   \\
15.000 &   1.465 -1.70e-1 &   1.455 -1.82e-1 &   1.436 -2.04e-1  &  1.379 -2.72e-1   \\
16.400 &   1.705 -1.42e-1  &  1.687 -1.57e-1 &   1.653 -1.84e-1  &  1.547 -2.67e-1   \\
17.200 &   1.945 -1.98e-1  &  1.916 -2.10e-1  &  1.853 -2.32e-1  &  1.699 -2.99e-1   \\
18.000  &   1.878 -1.61e-1 &   1.855 -1.74e-1 &   1.811 -1.99e-1 &   1.678 -2.77e-1  \\
18.500   &  1.787 -1.55e-1 &   1.768 -1.69e-1 &   1.737 -1.94e-1 &   1.636 -2.72e-1   \\
20.000 &   1.988 -2.20e-1  &  1.962 -2.29e-1 &   1.914 -2.45e-1  &  1.765 -2.96e-1   \\
21.300 &   1.973 -2.45e-1  &  1.948 -2.52e-1  &  1.903 -2.65e-1  &  1.761 -3.04e-1   \\
22.500 &   1.978 -2.52e-1  &  1.946 -2.58e-1 &   1.902 -2.69e-1 &   1.766 -3.04e-1   \\
25.000 &   1.907 -2.68e-1  &  1.888 -2.73e-1 &   1.852 -2.81e-1 &   1.742 -3.07e-1   \\
27.900 &   1.855 -2.99e-1  &  1.839 -3.01e-1 &   1.810 -3.05e-1 &   1.721 -3.16e-1   \\
30.000 &   1.814 -3.36e-1  &  1.800 -3.36e-1  &  1.776 -3.35e-1  &  1.698 -3.32e-1   \\
35.000 &   1.914 -4.30e-1  &  1.894 -4.25e-1  &  1.858 -4.16e-1  &  1.746 -3.89e-1   \\
40.000 &   1.932 -5.30e-1  &  1.911 -5.23e-1  &  1.872 -5.09e-1  &  1.761 -4.66e-1  \\
\hline
\end{tabular}
\caption{Long wavelength values of the complex refractive index of the small rural aerosol mode at low humidity}
\end{table}
\end{center}

\begin{center}
\begin{table}
\begin{tabular}{| c | c | c | c | c |  }
\hline
 $\lambda \mu m$   & 90\%  & 95\%  & 98\%  & 99\% \\
\hline
0.2000 &  1.441 -2.35e-2 &    1.431 -1.61e-2  & 1.421 -1.28e-2 & 1.415 -9.71e-3 \\
0.2500  &   1.418 -1.01e-2  &  1.405 -7.76e-3  &  1.393 -5.51e-3  &  1.385 -4.16e-3 \\
0.3300  &    1.410 -2.69e-3 & 1.396 -2.07e-3   & 1.382 -1.47e-3  &  1.374 -1.11e-3 \\
0.3371   &  1.407 -1.98e-3  &  1.393 -1.53e-3  &  1.379 -1.08e-3 &   1.371 -8.19e-4 \\
0.4000   &  1.403 -1.98e-3 &   1.388 -1.53e-3  &  1.374 -1.08e-3  &  1.366 -8.19e-4 \\
0.4880  &   1.401 -1.98e-3  &  1.385 -1.53e-3  &  1.371 -1.08e-3  &  1.362 -8.19e-4 \\
0.5145  &    1.400 -1.98e-3  &  1.385 -1.53e-3  &  1.370 -1.08e-3 &   1.361 -8.19e-4 \\
0.5500  &  1.399 -2.22e-3 &   1.384 -1.71e-3  &  1.369 -1.21e-3   & 1.360 -9.16e-4 \\
0.6328   &   1.399 -2.22e-3  &  1.383 -1.71e-3  &  1.368 -1.21e-3 &   1.359 -9.16e-4 \\
0.6943  &    1.398 -2.45e-3 &   1.383 -1.89e-3  &  1.368 -1.34e-3 &   1.359 -1.01e-3 \\
0.8600   &   1.393 -3.63e-3  &  1.378 -2.79e-3  &  1.364 -1.98e-3  &  1.356 -1.50e-3 \\
1.0600     &  1.391 -4.81e-3  &  1.376 -3.70e-3 & 1.362 -2.63e-3   & 1.353 -1.99e-3  \\
1.3000   &  1.381 -5.53e-3  &  1.367 -4.27e-3 & 1.355 -3.44e-3  &  1.347 -2.31e-3 \\
1.5360  &   1.371 -6.28e-3  &  1.359 -4.86e-3  &  1.347 -4.48e-3  &  1.340 -2.65e-3 \\
1.8000  &    1.349 -4.88e-3  &  1.340 -3.78e-3  &  1.332 -2.72e-3 &   1.327 -2.08e-3 \\
2.0000   &   1.328 -3.52e-3 &   1.323 -2.88e-3  &  1.318 -2.37e-3  &  1.315 -2.06e-3 \\
2.2500   &   1.315 -3.52e-3 &   1.310 -2.80e-3  &  1.304 -2.10e-3  &  1.301 -1.68e-3 \\
2.5000  &    1.290 -4.89e-3  &  1.283 -4.16e-3  &  1.277 -3.46e-3  &  1.273 -3.04e-3 \\
2.7000  &    1.237 -2.69e-2  &  1.226 -2.50e-2  &  1.225 -2.33e-2  &  1.208 -2.22e-2 \\
3.0000  &    1.361 -1.87e-1  &  1.364 -2.07e-1  &  1.366 -2.26e-1  &  1.367 -2.37e-1 \\
3.2000  &    1.441 -6.42e-2 &   1.449 -7.07e-2  &  1.458 -7.70e-2  &  1.463 -8.08e-2 \\
3.3923  &    1.408 -1.65e-2 &   1.411  1.74e-2  &  1.414 -1.83e-2  &  1.416 -1.88e-2 \\
3.5000   &   1.400 -8.53e-3 &   1.400 -8.73e-3  &  1.406 -8.92e-3 &   1.400 -9.04e-3 \\
3.7500   &   1.379 -4.37e-3 &   1.376 -4.17e-3 &   1.374 -3.98e-3  &  1.373 -3.86e-3 \\
4.0000   &   1.366 -5.44e-3 &   1.363 -5.25e-3  &  1.358 -5.06e-3  &  1.357 -4.95e-3 \\
4.5000  &   1.355 -1.34e-2  &  1.350 -1.34e-2  &  1.344 -1.34e-2  &  1.341 -1.34e-2 \\
5.0000  &   1.347 -1.27e-2 &   1.342 -1.26e-2  &  1.337 -1.25e-2  &  1.334 -1.25e-2 \\
5.5000   &   1.324 -1.41e-2  &  1.318 -1.35e-2 &   1.312 -1.29e-2 &   1.309 -1.26e-2 \\
6.0000   &   1.288 -8.02e-2  &  1.282 -8.64e-2 &   1.277 -9.24e-2  &  1.274 -9.59e-2 \\
6.2000   &   1.356 -6.87e-2  &  1.358 -7.32e-2 &   1.359 -7.75e-2  &  1.360 -8.00e-2 \\
6.5000  &    1.346 -3.90e-2  &  1.345 -3.83e-2  &  1.343 -3.86e-2  &  1.342 -3.87e-2 \\
7.2000  &    1.342 -4.33e-2  &  1.335 -4.07e-2  &  1.326 -3.82e-2  &  1.324 -3.87e-2 \\
\hline
\end{tabular}
\caption{Short wavelength values of the complex refractive index of the small rural aerosol mode at high humidity}
\end{table}
\end{center}

\begin{center}
\begin{table}
\begin{tabular}{| c | c | c | c | c |  }
\hline
 $\lambda \mu m$   & 90\%  & 95\%  & 98\%  & 99\% \\
\hline
7.9000  &   1.257 -4.18e-2  &  1.266 -4.00e-2   & 1.274 -3.82e-2  &  1.279 -3.72e-2 \\
8.2000  &    1.205 -5.43e-2 &   1.224 -4.99e-2  &  1.242 -4.56e-2  &  1.253 -4.30e-2 \\
8.5000  &   1.285 -8.40e-2  &  1.284 -7.31e-2  &  1.282 -6.25e-2  &  1.281 -5.62e-2 \\
8.7000  &  1.550 -1.03e-1  &  1.486 -8.83e-2  &  1.424 -7.37e-2  &  1.387 -6.49e-2 \\
9.0000   &   1.611 -1.28e-1  &  1.531 -1.07e-1 &   1.453 -8.78e-2  &  1.406 -7.61e-2 \\
9.2000   &   1.524 -1.41e-1  &  1.462 -1.18e-1  &  1.402 -9.61e-2  &  1.366 -8.28e-2 \\
9.5000   &   1.458 -8.34e-2 &   1.409 -7.44e-2 &   1.361 -6.57e-2  &  1.332 -6.05e-2 \\
9.8000   &   1.431 -7.05e-2 &   1.385 -6.63e-2  &  1.339 -6.02e-2  &  1.313 -5.72e-2 \\
10.000   &   1.431 -7.12e-2 &   1.368 -6.65e-2  &  1.325 -6.20e-2  &  1.299 -5.92e-2 \\
10.591   &   1.360 -7.33e-2 &   1.318 -7.20e-2  &  1.278 -7.06e-2 &  1.254 -6.92e-2 \\
11.000   &   1.333 -8.66e-2 &   1.292 -8.90e-2 &   1.252 -9.12e-2 &   1.228 -9.26e-2 \\
11.500   &   1.301 -1.15e-1  &  1.260 -1.22e-1 &   1.221 -1.27e-1 &   1.198 -1.31e-1 \\
12.500   &   1.279 -1.94e-1  &  1.243 -2.09e-1 &   1.208 -2.23e-1 &   1.187 -2.32e-1 \\
13.000   &   1.290 -2.26e-1  &  1.257 -2.44e-1  &  1.225 -2.62e-1 &   1.206 -2.72e-1 \\
14.000   &   1.324 -2.71e-1  &  1.297 -2.94e-1  &  1.272 -3.16e-1  &  1.257 -3.29e-1 \\
14.800   &   1.332 -2.97e-1  &  1.315 -3.20e-1 &   1.299 -3.42e-1 &   1.289 -3.55e-1 \\
15.000   &   1.336 -3.24e-1  &  1.320 -3.42e-1 &   1.306 -3.52e-1 &   1.297 -3.70e-1 \\
16.400   &   1.467 -3.31e-1  &  1.439 -3.53e-1 &   1.412 -3.75e-1 &   1.396 -3.87e-1 \\
17.200   &   1.574 -3.51e-1  &  1.531 -3.69e-1 &   1.489 -3.87e-1  &  1.464 -3.97e-1 \\
18.000   &   1.576 -3.37e-1  &  1.541 -3.57e-1  &  1.507 -3.77e-1 &   1.486 -3.89e-1 \\
18.500   &   1.559 -3.32e-1  &  1.532 -3.52e-1 &   1.506 -3.72e-1 &   1.491 -3.84e-1 \\
20.000   &  1.651 -3.35e-1   & 1.611 -3.48e-1 &   1.573 -3.61e-1  &  1.550 -3.69e-1 \\
21.300   &  1.653 -3.34e-1  &  1.616 -3.45e-1 &   1.579 -3.55e-1  &  1.558 -3.61e-1 \\
22.500   &   1.662 -3.39e-1 &   1.626 -3.39e-1 &   1.591 -3.48e-1  &  1.570 -3.54e-1 \\
25.000   &   1.657 -3.26e-1 &   1.628 -3.33e-1 &   1.606 -3.40e-1  &  1.583 -3.44e-1 \\
27.900   &   1.652 -3.25e-1 &   1.628 -3.28e-1 &   1.605 -3.31e-1 &   1.591 -3.33e-1 \\
30.000    &  1.639 -3.31e-1  &  1.619 -3.30e-1  &  1.599 -3.29e-1   & 1.567 -3.29e-1 \\
35.000   &  1.660 -3.68e-1  &  1.631 -3.60e-1  &  1.602 -3.53e-1  &  1.585 -3.49e-1 \\
40.000   &  1.658 -4.34e-1  &  1.626 -4.22e-1  &  1.595 -4.12e-1  &  1.576 -4.05e-1 \\
\hline
\end{tabular}
\caption{Long wavelength values of the complex refractive index of the small rural aerosol mode at high humidity}
\end{table}
\end{center}

\begin{center}
\begin{table}
\begin{tabular}{| c | c | c | c | c |  }
\hline
 $\lambda \mu m$   & 0\%  & 50\%  & 70\%  & 80\% \\
\hline
0.2000 & 1.530 -7.00e-2  &  1.523   -6.64e-2  &  1.508   -5.83e-2  &   1.461   -3.39e-2    \\  
0.2500 &  1.530 -3.00e-2 &  1.521   -2.84e-2 &   1.502   -2.50e-2  &   1.443   -1.45e-2   \\  
0.3300 &  1.530 -6.00e-3 &  1.521   -7.59e-3  &  1.500   -6.66e-3  &   1.437   -3.87e-3     \\ 
0.3371 &  1.530 -5.90e-3 &  1.520   -5.59e-3  &  1.499   -4.91e-3  &   1.435   -2.86e-3    \\
0.4000 &  1.530 -5.90e-3 &  1.520   -5.59e-3 &   1.498   -4.91e-3  &   1.431   -2.86e-3    \\
0.4880 &  1.530 -5.90e-3 &  1.520   -5.59e-3 &   1.497   -4.91e-3  &   1.429   -2.86e-3    \\
0.5145 &  1.530 -5.90e-3 &  1.520   -5.59e-3 &   1.497   -4.91e-3  &   1.429   -2.86e-3  \\
0.5500 &  1.530 -6.69e-3 &  1.520   -6.26e-3 &   1.497   -5.49e-3  &   1.428   -3.19e-3   \\
0.6328 &  1.530 -6.60e-3 &  1.520   -6.26e-3 &   1.497   -5.49e-3  &   1.428   -3.19e-3    \\
0.6943 &  1.530 -7.30e-3 &  1.520   -6.92e-3 &   1.497   -6.08e-3 &    1.427   -3.53e-3   \\
0.8600 &  1.520 -1.08e-2 &  1.510   -1.02e-2 &   1.488   -8.99e-3 &    1.421   -5.23e-3   \\
1.0600 &  1.528 -1.43e-2 &  1.510   -1.36e-2 &   1.487   -1.18e-2 &    1.420   -6.92e-3    \\
1.3000 &  1.495 -1.64e-2 &  1.486   -1.56e-2 &   1.466   -1.37e-2  &   1.406   -7.96e-3     \\
1.5360 &  1.477 -1.85e-2 &  1.469   -1.75e-2 &   1.450   -1.54e-2 &    1.395   -9.01e-3    \\
1.8000 &  1.421 -1.43e-2 &  1.415   -1.36e-2 &   1.403   -1.19e-2  &   1.365   -6.98e-3    \\
2.0000 &  1.372 -8.00e-3 &  1.369   -7.64e-3 &   1.361   -6.84e-3  &   1.338   -4.44e-3     \\
2.2500 &  1.360 -9.70e-3 &  1.356   -8.22e-3 &   1.349   -8.14e-3  &   1.325   -4.90e-3    \\
2.5000 &  1.348 -1.11e-2 &  1.343   -1.06e-2 &   1.333   -9.53e-3 &    1.303   -6.27e-3   \\
2.7000 &  1.334 -4.24e-2 &  1.326   -4.12e-2 &   1.310   -3.85e-2 &    1.259   -3.03e-2     \\
3.0000 &  1.342 -1.90e-2 &  1.344   -3.21e-2 &   1.347   -6.14e-2 &    1.357   -1.50e-1    \\
3.2000 &  1.367 -8.60e-3 &  1.373   -1.29e-2 &   1.386   -2.26e-2 &    1.424   -5.18e-2    \\
3.3923 &  1.379 -8.80e-3 &  1.381   -8.40e-3 &   1.386   -1.07e-2 &    1.401   -1.48e-2    \\
3.5000 &  1.399 -6.80e-3 &  1.399   -6.39e-3 &   1.399   -7.24e-3 &    1.400   -8.14e-3   \\
3.7500 &  1.397 -6.20e-3 &  1.396   -5.97e-3 &   1.393   -5.66e-3 &    1.383   -4.76e-3    \\
4.0000 &  1.397 -7.10e-3 &  1.394   -6.97e-3 &   1.389   -6.88e-3 &    1.373   -5.81e-3    \\
4.5000 &  1.400 -1.33e-2 &  1.396   -1.33e-2 &   1.389   -1.33e-2 &    1.365   -1.34e-2    \\
5.0000 &  1.390 -1.32e-2 &  1.387   -1.32e-2 &   1.379   -1.31e-2 &    1.356   -1.28e-2   \\
5.5000 &  1.374 -1.89e-2 &  1.370   -1.85e-2 &   1.361   -1.77e-2 &    1.335   -1.51e-2    \\
6.0000 &  1.332 -2.72e-2  & 1.329   -3.13e-2 &   1.321   -4.06e-2 &    1.297   -6.84e-2   \\
6.2000 &  1.343 -3.06e-2 &  1.344   -3.36e-2 &   1.346   -4.02e-2  &   1.353   -6.02e-2    \\
6.5000 &  1.361 -3.57e-2 &  1.360   -3.59e-2 &   1.357   -3.63e-2 &    1.350   -3.75e-2     \\
7.2000&   1.400 -6.55e-2 &  1.395   -6.38e-2 &   1.385   -5.59e-2  &   1.355   -4.83e-2   \\
\hline
\end{tabular}
\caption{Short wavelength values of the complex refractive index of the large rural aerosol mode at low humidity}
\end{table}
\end{center}

\begin{center}
\begin{table}
\begin{tabular}{| c | c | c | c | c |  }
\hline
 $\lambda \mu m$   & 0\%  & 50\%  & 70\%  & 80\% \\
\hline
7.9000 &  1.185 -5.75e-2 &  1.191   -5.63e-2 &   1.203   -5.35e-2  &   1.241   -4.53e-2     \\
8.2000 &  1.046 -9.33e-2 &  1.058   -8.92e-2 &   1.086   -8.26e-2  &   1.170   -6.27e-2     \\
8.5000 &  1.300 -1.78e-1 &  1.299   -1.70e-1 &   1.296   -1.54e-1  &   1.289   -1.05e-1     \\
8.7000 &  2.100 -2.33e-1 &  2.057   -2.23e-1 &   1.961   -2.00e-1  &   1.673   -1.32e-1    \\
9.0000 &  2.302 -3.01e-1 &  2.248   -2.87e-1 &   2.128   -2.57e-1  &   1.765   -1.66e-1     \\
9.2000 &  2.056 -3.39e-1 &  2.015   -3.24e-1 &   1.922   -2.89e-1  &   1.643   -1.85e-1     \\
9.5000 &  1.884 -1.61e-1 &  1.851   -1.55e-1 &   1.777   -1.41e-1  &   1.553   -1.01e-1     \\
9.8000 &  1.831 -1.15e-1 &  1.800   -1.12e-1 &   1.730   -1.04e-1  &   1.520   -8.04e-2     \\
10.000 &  1.799 -1.12e-1 &  1.769   -1.08e-1  &  1.702   -1.01e-1  &   1.499   -8.02e-2     \\
10.591 &  1.718 -8.50e-2 &  1.690   -8.41e-2 &   1.628   -8.21e-2  &   1.440   -7.59e-2     \\
11.000 &  1.690 -6.65e-2 &  1.662   -6.81e-2 &   1.600   -7.16e-2  &   1.413   -8.21e-2    \\
11.500 &  1.646 -6.29e-2 &  1.619   -6.70e-2 &   1.559   -7.62e-2  &   1.378   -1.04e-1     \\
12.500 &  1.587 -6.41e-2 &  1.563   -7.42e-2 &   1.509   -9.68e-2   &  1.348   -1.65e-1    \\
13.000 &  1.575 -6.85e-2 &  1.553   -8.07e-2 &   1.593   -1.08e-1  &   1.354   -1.91e-1     \\
14.000 &  1.548 -7.66e-2 &  1.531   -9.18e-2 &   1.491   -1.26e-1  &   1.374   -2.28e-1     \\
14.800 &  1.479 -1.00e-1 &  1.468   -1.15e-1 &   1.442   -1.50e-1  &   1.365   -2.53e-1    \\
15.000 &  1.465 -1.70e-1 &  1.455   -1.82e-1 &   1.432   -2.09e-1  &   1.364   -2.90e-1   \\
16.400 &  1.705 -1.42e-1 &  1.686   -1.57e-1 &   1.645   -1.90e-1  &   1.520   -2.89e-1    \\
17.200 &  1.945 -1.98e-1 &  1.916   -2.10e-1 &   1.851   -2.37e-1  &   1.657   -3.17e-1   \\
18.000 &  1.878 -1.61e-1 &  1.854   -1.74e-1 &   1.802   -2.05e-1  &   1.643   -2.98e-1     \\
18.500 & 1.787 -1.55e-1 &  1.769   -1.69e-1  &  1.729   -2.00e-1   &  1.609   -2.92e-1     \\
20.000 &  1.988 -2.20e-1 &  1.962   -2.28e-1 &   1.903   -2.49e-1  &   1.726   -3.00e-1     \\
21.300 &  1.973 -2.45e-1 &  1.948   -2.52e-1 &   1.892   -2.68e-1  &   1.724   -3.14e-1     \\
22.500 &  1.978 -2.52e-1 &  1.946   -2.58e-1 &   1.892   -2.72e-1  &   1.731   -3.13e-1     \\
25.000 &  1.907 -2.68e-1 &  1.888   -2.73e-1 &   1.844   -2.83e-1  &   1.713   -3.13e-1    \\
27.900 &  1.855 -2.99e-1 &  1.839   -2.01e-1 &   1.804   -3.06e-1  &   1.697   -3.19e-1    \\
30.000 &  1.814 -3.36e-1 &  1.800   -3.36e-1 &   1.770   -3.35e-1  &   1.678   -3.32e-1     \\
35.000 &  1.914 -4.30e-1 &  1.894   -4.25e-1 &   1.850   -4.14e-1  &   1.717   -3.81e-1     \\
40.000 &  1.932 -5.30e-1 &  1.911   -5.22e-1 &   1.863   -5.16e-1  &   1.719   -4.55e-1    \\
\hline
\end{tabular}
\caption{Long wavelength values of the complex refractive index of the large rural aerosol mode at low humidity}
\end{table}
\end{center}

\begin{center}
\begin{table}
\begin{tabular}{| c | c | c | c | c |  }
\hline
 $\lambda \mu m$   & 90\%  & 95\%  & 98\%  & 99\% \\
\hline
0.2000  &   1.435   -2.06e-2 &   1.426   -1.57e-2  &  1.408   -6.04e-3 &   1.403   -3.43e-3  \\
0.2500  &   1.411   -8.84e-3 &   1.400   -6.73e-3  &  1.377   -2.59e-3 &   1.370   -1.47e-3  \\
0.3300  &   1.402   -2.36e-3 &   1.390   -1.79e-3  &  1.365   -6.91e-4 &   1.358   -3.92e-4  \\
0.3371  &   1.400   -1.74e-3 &   1.386   -1.32e-3  &  1.361   -5.09e-4 &   1.354   -2.89e-4  \\
0.4000  &   1.395   -1.74e-3 &   1.382   -1.32e-3  &  1.355   -5.09e-4 &   1.348   -2.89e-4  \\
0.4880  &   1.392   -1.74e-3 &   1.379   -1.32e-3  &  1.352   -5.09e-4 &   1.345   -2.89e-4  \\
0.5145  &   1.392   -1.74e-3 &   1.378   -1.32e-3   & 1.351   -5.09e-4 &   1.344   -2.89e-4  \\
0.5500   &  1.391   -1.94e-3 &   1.377   -1.48e-3  &  1.350   -5.70e-4 &   1.343   -3.23e-4  \\
0.6328  &   1.390   -1.94e-3 &   1.376   -1.48e-3  &  1.349   -5.70e-4 &   1.342   -3.23e-4  \\
0.6943  &   1.390   -2.15e-3 &   1.376   -1.64e-3  &  1.348   -6.30e-4 &   1.341   -3.57e-4  \\
0.8600  &   1.385   -3.18e-3 &   1.372   -2.42e-3  &  1.345   -9.33e-4 &   1.338   -5.29e-4  \\
1.0600  &   1.383   -4.22e-3 &   1.369   -3.21e-3  &  1.343   -1.24e-3 &   1.335   -7.04e-4  \\
1.3000   &  1.374   -4.86e-3 &   1.362   -3.71e-3  &  1.338   -1.45e-3 &   1.331   -8.38e-4  \\
1.5360   &  1.365   -5.52e-3 &   1.354   -4.23e-3  &  1.332   -1.69e-3 &   1.326   -1.00e-3  \\
1.8000  &   1.344   -4.29e-3 &   1.336   -3.30e-3  &  1.321   -1.34e-3 &   1.317   -8.09e-4  \\
2.0000  &   1.325   -3.13e-3 &   1.321   -2.65e-3  &  1.312   -1.70e-3 &   1.309   -1.04e-3  \\
2.2500  &   1.312   -3.13e-3 &   1.307   -2.48e-3  &  1.298   -1.19e-3 &   1.295   -8.46e-4  \\
2.5000 &    1.287   -4.50e-3 &   1.281   -3.84e-3 &   1.269   -2.55e-3 &   1.265   -2.20e-3  \\
2.7000 &    1.231   -2.59e-2 &   1.221   -2.52e-2 &   1.201   -2.10e-2 &   1.195   -2.01e-2  \\
3.0000 &    1.362   -1.97e-1 &   1.364   -2.15e-1 &   1.368   -2.50e-1 &   1.370   -2.60e-1  \\
3.2000 &    1.445   -6.77e-2 &   1.353   -7.36e-2 &   1.468   -8.52e-2 &   1.473   -8.83e-2  \\
3.3923 &    1.409   -1.70e-2 &   1.412   -1.78e-2 &   1.418   -1.94e-2 &   1.420   -1.98e-2  \\
3.5000 &    1.400   -8.63e-3 &   1.400   -8.82e-3 &   1.400   -9.18e-3 &   1.400   -9.27e-3  \\
3.7500 &    1.377   -4.27e-3 &   1.375   -4.08e-3 &   1.371   -3.72e-3 &   1.370   -3.63e-3  \\
4.0000 &    1.364   -5.34e-3 &   1.361   -5.16e-3 &   1.355   -4.82e-3 &   1.353   -4.72e-3  \\
4.5000 &    1.352   -1.34e-2  &  1.347   -1.34e-2 &   1.338   -1.34e-2 &   1.335   -1.34e-2  \\
5.0000 &    1.344   -1.26e-2 &   1.340   -1.26e-2 &   1.331   -1.25e-2 &   1.328   -1.24e-2  \\
5.5000 &    1.320   -1.38e-2  &  1.315   -1.32e-2  &  1.305   -1.22e-2 &   1.302   -1.20e-2  \\
6.0000 &    1.285   -8.35e-2 &   1.280   -8.91e-2 &   1.271   -1.00e-1  &  1.268   -1.03e-1  \\
6.2000 &    1.387   -7.11e-2 &   1.359   -7.51e-2 &   1.361   -8.32e-2  &  1.362   -8.52e-2  \\
6.5000 &    1.345   -3.82e-2 &   1.344   -3.84e-2 &   1.341   -3.89e-2  &  1.340   -3.90e-2  \\
7.2000 &    1.338   -4.19e-2 &   1.332   -3.96e-2 &   1.320   -3.50e-2  &  1.316   -3.37e-2  \\
\hline
\end{tabular}
\caption{Short wavelength values of the complex refractive index of the large rural aerosol mode at high humidity}
\end{table}
\end{center}

\begin{center}
\begin{table}
\begin{tabular}{| c | c | c | c | c |  }
\hline
 $\lambda \mu m$   & 90\%  & 95\%  & 98\%  & 99\% \\
\hline
7.9000 &    1.262   -4.09e-2 &   1.270   -3.92e-2  &  1.285   -3.59e-2  &  1.289   -3.51e-2  \\
8.2000 &    1.215   -5.19e-2 &   1.232   -4.79e-2  &  1.265   -4.00e-2  &  1.274   -3.79e-2  \\
8.5000 &    1.284   -7.81e-2  &  1.283   -6.12e-2 &   1.280   -4.88e-2  &  1.279   -4.35e-2  \\
8.7000 &    1.516   -9.53e-2  &  1.458   -8.16e-2 &   1.344   -5.47e-2  &  1.313   -4.74e-2  \\
9.0000 &    1.568   -1.17e-1  &  1.495   -9.84e-2 &   1.352   -6.24e-2 &   1.313   -5.27e-2  \\
9.2000 &    1.491   -1.29e-1  &  1.435   -1.08e-1 &   1.324   -6.72e-2 &   1.294   -5.61e-2  \\
9.5000 &    1.432   -7.86e-2  &  1.387   -7.04e-2 &   1.298   -5.44e-2 &   1.274   -5.00e-2  \\
9.8000 &    1.406   -6.77e-2 &   1.364   -6.30e-2 &   1.281   -5.37e-2  &  1.258   -5.12e-2  \\
10.000 &    1.389   -6.87e-2 &   1.348   -6.44e-2  &  1.268   -5.61e-2 &   1.246   -5.38e-2  \\
10.591 &    1.338   -7.26e-2 &   1.300   -7.14e-2 &   1.226   -6.89e-2  &  1.205   -6.83e-2  \\
11.000 &    1.311   -8.79e-2 &   1.273   -9.00e-2 &   1.199   -9.42e-2  &  1.179   -9.53e-2  \\
11.500 &   1.279   -1.19e-1  &  1.243   -1.24e-1  &  1.171   -1.35e-1  &  1.151   -1.38e-1  \\
12.500 &    1.260   -2.02e-1 &   1.227   -2.15e-1  &  1.163   -2.42e-1  &  1.146   -2.49e-1  \\
13.000  &   1.272   -2.35e-1 &   1.242   -2.52e-1  &  1.183   -2.85e-1  &  1.167   -2.93e-1  \\
14.000  &   1.316   -2.84e-1 &   1.286   -3.04e-1 &   1.239   -3.45e-1  &  1.227   -3.56e-1  \\
14.800  &   1.323   -3.09e-1 &   1.308   -3.30e-1  &  1.277   -3.71e-1  &  1.269   -3.82e-1  \\
15.000  &   1.327   -3.34e-1 &   1.314   -3.50e-1 &   1.287   -3.82e-1  &  1.280   -3.91e-1  \\
16.400  &   1.452   -3.43e-1 &   1.426   -3.63e-1  &  1.377   -4.02e-1  &  1.364   -4.13e-1  \\
17.200  &   1.551   -3.61e-1  &  1.511   -3.77e-1 &   1.434   -4.09e-1 &   1.413   -4.18e-1  \\
18.000  &   1.557   -3.48e-1 &   1.525   -3.66e-1 &   1.462   -4.03e-1 &   1.445   -4.13e-1  \\
18.500  &   1.544   -3.43e-1 &   1.520   -3.61e-1 &   1.473   -3.98e-1 &   1.460   -4.08e-1  \\
20.000  &   1.630   -3.42e-1 &   1.594   -3.54e-1  &  1.524   -3.78e-1 &   1.505   -3.85e-1  \\
21.300  &   1.633   -3.40e-1  &  1.599   -3.49e-1 &   1.533   -3.68e-1 &   1.515   -3.73e-1  \\
22.500  &   1.643   -3.35e-1  &  1.610   -3.44e-1 &   1.546   -3.60e-1  &  1.529   -3.64e-1  \\
25.000  &   1.642   -3.30e-1  &  1.615   -3.46e-1 &   1.563   -3.48e-1  &  1.549   -3.52e-1  \\
27.900  &   1.639   -3.27e-1  &  1.618   -3.30e-1 &   1.575   -3.35e-1  &  1.564   -3.37e-1  \\
30.000  &   1.628   -3.30e-1 &   1.610   -3.30e-1 &   1.574   -3.29e-1  &  1.564   -3.28e-1  \\
35.000  &   1.654   -3.64e-1 &   1.618   -3.57e-1  &  1.565   -3.44e-1  &  1.561   -3.41e-1  \\
40.000  &   1.642   -4.28e-1 &   1.612   -4.18e-1  &  1.555   -3.98e-1  &  1.539   -3.92e-1 \\
\hline
\end{tabular}
\caption{Long wavelength values of the complex refractive index of the large rural aerosol mode at high humidity}
\end{table}
\end{center}

As a note of caution, these data were typed on a bad typwriter in the original data (some characters are difficult
to read) and were entered manually by the author. Errors are quite possible, however that may be, the do not lead to
large error in extinction coefficient as a function of wavelength.


\bibliography{/home/daddio/Articles/Mybib}
%\newpage
%\vspace*{20cm}
%\begin{figure}[htb]
%\special{psfile=Dodec.eps vscale=50 hscale=50 voffset=10 hoffset=10}
%\caption{ 
%A computer perspective drawing of the dodecahedron.
%}
%\end{figure}

\end{document}

